Optimal (Multiway) Spatial Joins

### 2024-05-29 msj.tex
yufei

We argue that the $k$-tuple $(r_1, ..., r_{k-2}, h, v)$ belongs to $\J(R_1,...,$ $R_{k-2},H,V)$. Clearly, $r_z$ covers $\bm{t}[z]$ for all $z \in [k-2]$. Thus, $\bigcap_{z=1}^{k-2} r_z$ covers $\bigcap_{z=1}^{k-2} \bm{t}[z]$, which is $B_\bm{t}$. Hence, point $p$ --- which is the intersection point of $h$ and $v$ and a corner of $B_\bm{t}$ --- falls in $\bigcap_{z=1}^{k-2} r_z$, indicating that $h \cap v \cap \bigcap_{z=1}^{k-2} r_z \ne \emptyset$. We now map $\bm{t}$ to $(r_1, ..., r_{k-2}, h, v)$.

>>>>

We argue that the $k$-tuple $(r_1, ..., r_{k-2}, h, v)$ belongs to $\J(R_1,...,$ $R_{k-2},H,V)$. Clearly, $r_z$ covers $\bm{t}[z]$ for all $z \in [k-2]$. Thus, $\bigcap_{z=1}^{k-2} r_z$ covers $\bigcap_{z=1}^{k-2} \bm{t}[z]$, which is $B_\bm{t}$. Hence, point $p$ --- which is the intersection point of $h$ and $v$ and a corner of $B_\bm{t}$ --- falls in $\bigcap_{z=1}^{k-2} r_z$, indicating $h \cap v \cap \bigcap_{z=1}^{k-2} r_z \ne \emptyset$. We map $\bm{t}$ to $(r_1, ..., r_{k-2}, h, v)$.
